### 2017-05-10 sheets/basis-2/sheet-basis-2.tex
Some changes to order and fixes of typos.

\section{Maps between Categories -- Functors}

\begin{exercise}
  Let $A$ and $B$ be posets, and $\A$ and $\B$ be the corresponding categories. Show that a contravariant functor $F:\A\rightarrow \B$ corresponds (uniquely) to a monotonically increasing function $f:A\rightarrow B$
\end{exercise}

@@

\begin{definition}{Coslice Category}
  Let $\A$ be a category and $A\in\ob(\A)$ an object. The \emph{coslice category} $A/\A$ of $\A$ under $A$ consists of
  \begin{itemize}
  \item the arrows to $A$ (i.e. the codomain of which are $A$) as objects
  \item and for $f\in \A(A,B)$, $g\in\A(A',B)$ (which are objects in $A/\A$) the arrows between $f$ and $g$ in $A/\A$ are arrows $h$ such that $h\of f=g$.
  \end{itemize}
\end{definition}

\begin{definition}{$\mathbf{Sets_*}$}
  The category $\mathbf{Sets_*}$ of \emph{pointed sets} consists of
  \begin{itemize}
  \item pairs $(A,a)$ such that $A$ is a set and $a\in A$ as objects and
  \item arrows objects between objects $(A,a)$ and $(B,b)$ are functions $f\from A\to B$ such that $f(a)=b$.
  \end{itemize}
\end{definition}

\begin{definition}{Slice Category}
  Let $\A$ be a category and $A\in\ob(\A)$ an object. The \emph{slice category} $\A/A$ of $\A$ over $A$ consists of
  \begin{itemize}
  \item the arrows from $A$ (i.e. the domain of which are $A$) as objects
  \item and for $f\in \A(A,B)$, $g\in\A(A',B)$ (which are objects in $A/\A$) the arrows between $f$ and $g$ in $A/\A$ are arrows $h$ such that $g\of h=f$.
  \end{itemize}
\end{definition}

\begin{exercise}[\textit{Challenge}]
  Let $\A$ be a category. Construct a functor $F\from \A\to\mathbf{Cat}$ such that $F(A)=\A/A$ and show that this indeed a functor. Is this also an isomorphism?

\begin{exercise}
  Find interesting examples for a functor that is both full and faithful, one that is full but not faithful, one that is fathful but not full, and one that is neither.
\end{exercise}

\begin{exercise}
  \begin{enumerate}
    \item Define an endofunctor on $\Set$ that maps every set to its powerset.
      Check that is satisfies the functor laws.
      Is it full/faithful?
    \item Define a contravariant endofunctor on $\Set$, i.e.\ a functor from $\Set^\op$ to $\Set$, that maps every set to its powerset.
      Check that is satisfies the functor laws.
      Is it full/faithful?
  \end{enumerate}
\end{exercise}

@@

>>>>

\begin{exercise}
  Find interesting examples for a functor that is both full and faithful, one that is full but not faithful, one that is faithful but not full, and one that is neither.
\end{exercise}

\begin{exercise}
  \begin{enumerate}
    \item Define an endofunctor on $\Set$ that maps every set to its powerset.
      Check that it satisfies the functor laws.
      Is it full/faithful?
    \item Define a contravariant endofunctor on $\Set$, i.e.\ a functor from $\Set^\op$ to $\Set$, that maps every set to its powerset.
      Check that it satisfies the functor laws.
      Is it full/faithful?
  \end{enumerate}
\end{exercise}

\begin{exercise}
  Let $A$ and $B$ be posets, and $\A$ and $\B$ be the corresponding categories. Consider a contravariant functor $F:\A\rightarrow \B$. Describe properties of the corresponding function $f:A\rightarrow B$.
\end{exercise}

@@

@@

\begin{definition}{Coslice Category}
  Let $\A$ be a category and $A\in\ob(\A)$ an object. The \emph{coslice category} $A/\A$ of $\A$ under $A$ consists of
  \begin{itemize}
  \item the arrows to $A$ (i.e. the domain of which is $A$) as objects
  \item and for $f\in \A(A,B)$, $g\in\A(A,B')$ (which are objects in $A/\A$) the arrows between $f$ and $g$ in $A/\A$ are arrows $h$ such that $h\of f=g$.
  \end{itemize}
\end{definition}

\begin{definition}{$\mathbf{Sets_*}$}
  The category $\mathbf{Sets_*}$ of \emph{pointed sets} consists of
  \begin{itemize}
  \item pairs $(A,a)$ such that $A$ is a set and $a\in A$ as objects and
  \item arrows between objects $(A,a)$ and $(B,b)$ are functions $f\from A\to B$ such that $f(a)=b$.
  \end{itemize}
\end{definition}

\begin{definition}{Slice Category}
  Let $\A$ be a category and $A\in\ob(\A)$ an object. The \emph{slice category} $\A/A$ of $\A$ over $A$ consists of
  \begin{itemize}
  \item the arrows from $A$ (i.e. the codomain of which is $A$) as objects
  \item and for $f\in \A(A,B)$, $g\in\A(A',B)$ (which are objects in $A/\A$) the arrows between $f$ and $g$ in $A/\A$ are arrows $h$ such that $g\of h=f$.
  \end{itemize}
\end{definition}

\begin{exercise}[\textit{Not entirely trivial 2}]
  Let $\A$ be a category. Construct a functor $F\from \A\to\mathbf{Cat}$ such that $F(A)=\A/A$ and show that this is indeed a functor. Is this also an isomorphism?
